A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-15 mt-marathon.2013/PBML_article.tex
changes

Each feature function is implemented in a separate class, with no common class hierarchy. The initialisation and evaluation of each feature function was entirely bespoked.

@@

The state information in Moses has evolved since inception. Initially, state information was only available from language models, therefore, only language models states are compared, Figure~\ref{algo:CompareHypoStates}.

@@

The state comparison routine of Figure~\ref{algo:CompareHypoStates} evolved to compare the state of all stateful feature functions, Figure~\ref{algo:CompareHypoStates.new}.

@@

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions are hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}:
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

@@

Equation~\ref{eq:translation rule score} becomes Equation~\ref{eq:translation rule score.new}
\begin{equation}
  score = \sum_{m \in FF} \sum_{i \in m} (\lambda_{m,i} * score_{m,i})
\label{eq:translation rule score.new}
\end{equation}
where $FF$ is the set of feature functions.

@@

Furthermore, there are three stages during decoding where each feature function can be evaluated:
\begin{enumerate}
    \item During creation of translation rules. Access to the words in the source and target side of translation rule.
    \item Just before decoding. Access to the entire source sentence to be decoded.
    \item During decoding. Access to the context information is available, containing the hypotheses create to translate the sentence so far. The exact information contained in the hypotheses is dependent on whether the formalism used.
\end{enumerate}
At each stage, a different range of information is available to the feature function to access for information. Scores that are evaluated at stage (1) can be cached and reused inter-sentence. Scores evaluted during stage (2) and (3) cannot be cached as they depend on the entire source sentence. Therefore, it is more efficient to evaluate as early as possible.

@@

On the other hand, a feature that depends on the bag of words of the input sentence would override the method for stage (2).

@@

The most efficient way to implement language models is to override stage (1) and (3). As a stateful feature, it must override stage (3) to access adjacent target words to score overlapping n-grams. However, it is able to score the n-grams within each translation rule, and also calculate the estimated future cost, without the context. By evaluating the stateless portion of the language model score during stage (1) mitigate these score from having to be re-evaluated each time the translation rule is applied. This behaviour codify the existing practises by building the framework to support it, alllowing other feature function to take advantage of this efficient mechanism.

Additionally, some feature functions do not override any of the stages. These feature is so intertwined with the search operation that their scores are set by search operation themselves. The feature function exist as an identifier to locate the score. Features functions such as the translation models, unknown word penalty, and generation models score fall into this category.

>>>>

Each feature function is implemented as a separate class, with no common class hierarchy. The initialisation and evaluation of each feature function was entirely bespoked.

@@

The state information in Moses has evolved since its inception. Initially, state information was only available for language models, therefore, only language models states are compared, Figure~\ref{algo:CompareHypoStates}.

@@

The state comparison routine of Figure~\ref{algo:CompareHypoStates} was generalised to compare the state of all stateful feature functions, Figure~\ref{algo:CompareHypoStates.new}.

@@

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The set of feature functions are hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}:
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

@@

Equation~\ref{eq:translation rule score} becomes Equation~\ref{eq:translation rule score.new}
\begin{equation}
  score = \sum_{m \in FF} \sum_{i \in m} (\lambda_{m,i} * score_{m,i})
\label{eq:translation rule score.new}
\end{equation}
where $FF$ is the set of all feature functions.

@@

Furthermore, there are three juncture during decoding where each feature function can be evaluated. At each point, a different range of information is available to the feature function. 
\begin{enumerate}
    \item During creation of translation rules. Has access to the words in the source and target side of translation rule, but not the entire input sentence.
    \item Just before decoding. Has access to the entire source sentence to be decoded.
    \item During decoding. Access to the context information is possible, containing the current and antecedent hypotheses. The exact information contained in the hypotheses is dependent on the formalism used.
\end{enumerate}
However, the stage at which the feature function is evaluate determines whether the feature function is cacheable between sentences. Scores that are evaluated at stage (1) can be cached and reused inter-sentence. Scores evaluated during stage (2) and (3) cannot be cached as they depend on the entire source sentence. Therefore, it is more efficient to evaluate as early as possible.

Additionally, some feature functions do not override any of the stages. These feature is so intertwined with the search operation that their scores are set by search operation themselves. The feature function exist as an identifier to locate the score. Features functions such as the translation models, unknown word penalty,  generation models, and input feature score fall into this category.

\subsection{Examples}

@@

On the other hand, a feature that depends on the bag of words of the input sentence must override the evaluation method for stage (2).

@@

The most efficient way to implement language models is to override stage (1) and (3). As a stateful feature, it must override stage (3) to access adjacent target words to score overlapping n-grams, and to set the current state. However, it is able to evaluate the n-grams within each translation rule without the context, therefore, language models should also override stage (1). The calculation of estimate future cost should also occur in stage (1). This behaviour codify existing practises by building the framework to support it, allowing other feature functions to take advantage of this efficient mechanism.
